Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-07-04 overall.tex
Address referee's comment based on Sergey's e-mail

\ifreview
Comments to address in this section:
\begin{enumerate}
    % \item REVIEWER 2: In Figure 4, there are some inconsistencies. The
    % figure caption shows there are only 62175 measures, but in the scatter
    % plot (right) there are 62555 data points. In addition, according to the
    % distribution of the number of work nodes (left), it does not look like
    % the mean number of work available is 691 as the figure caption
    % illustrates.
    \item REVIEWER 3: It’s interesting that Feb/March have such an increase
    in backfill availability in 2017. The authors attribute this to hardware
    upgrades for the DTNs. It’s mentioned that the load is only 3.6\% now and
    therefore further upgrades will likely not cause similar improvement.
    What was the previous CPU load? Why were particularly low percentages
    utilized in April/May 2016?
    % \item REVIEWER 4: “Genat4” at the end of Section 4 is a typo.
    % \item REVIEWER 4: Please explain why you used Titan at all, in spite of
    % your statement that it is 1/2 to 1/3 as efficient as other resources.
    % Was it merely that you were given so much time on this resource that
    % the inefficiency doesn’t matter?
    \item REVIEWER 4: Why didn’t you benchmark the performance of your
    workload on other HPC resources that might have delivered better
    performance, prior to reengineering your entire workflow to deal with the
    challenges posed by Titan, a machine that doesn’t seem to justify the
    pain?
    \item REVIEWER 4: The INCITE program operational requirements for the
    LCFs are 90\% uptime. Using large batches of Geant4 jobs that run on a
    single node or less to reach this metric sounds like gaming the system
    rather than an accomplishment.
    % \item REVIEWER 5: In Figure 3, it shows the unused core hours are much
    % higher than those used by ATLAS\@. What are the reasons for such low
    % usage?
\end{enumerate}
\fi

@@

On February 2017, PanDA Brokers used almost twice as much total backfill
availability than in any other month (preliminary results for March 2017
displayed in Fig.~\ref{fig:backfill-utilization} confirm this trend). No
relevant code update was made during that period and logs indicated that the
brokers were able to perform faster. This is likely due to hardware upgrades
on the DTNs. The absence of continuous monitoring of those nodes does not
allow to quantify bottlenecks but spot measurements of their load indicate
that a faster CPU and better networking were likely responsible for the
improved performance. Investigations showed an average CPU load of 3.6\% on
the upgraded DTNs. As such, further hardware upgrades seem unlikely to
improve significantly the performance of PanDA Brokers.\mtnote{Asked Segey
and Danila for values previous HW upgrade}

>>>>

\ifreview
Comments to address in this section:
\begin{enumerate}
    % \item REVIEWER 2: In Figure 4, there are some inconsistencies. The
    % figure caption shows there are only 62175 measures, but in the scatter
    % plot (right) there are 62555 data points. In addition, according to the
    % distribution of the number of work nodes (left), it does not look like
    % the mean number of work available is 691 as the figure caption
    % illustrates.
    \item 
    % REVIEWER 3: It’s interesting that Feb/March have such an increase in
    % backfill availability in 2017. The authors attribute this to hardware
    % upgrades for the DTNs. It’s mentioned that the load is only 3.6\% now
    % and therefore further upgrades will likely not cause similar
    % improvement. What was the previous CPU load? 
    Why were particularly low percentages utilized in April/May 2016?
    % \item REVIEWER 4: “Genat4” at the end of Section 4 is a typo.
    % \item REVIEWER 4: Please explain why you used Titan at all, in spite of
    % your statement that it is 1/2 to 1/3 as efficient as other resources.
    % Was it merely that you were given so much time on this resource that
    % the inefficiency doesn’t matter?
    \item REVIEWER 4: Why didn’t you benchmark the performance of your
    workload on other HPC resources that might have delivered better
    performance, prior to reengineering your entire workflow to deal with the
    challenges posed by Titan, a machine that doesn’t seem to justify the
    pain?
    \item REVIEWER 4: The INCITE program operational requirements for the
    LCFs are 90\% uptime. Using large batches of Geant4 jobs that run on a
    single node or less to reach this metric sounds like gaming the system
    rather than an accomplishment.
    % \item REVIEWER 5: In Figure 3, it shows the unused core hours are much
    % higher than those used by ATLAS\@. What are the reasons for such low
    % usage?
\end{enumerate}
\fi

@@

On February 2017, PanDA Brokers used almost twice as much total backfill
availability than in any other month (preliminary results for March 2017
displayed in Fig.~\ref{fig:backfill-utilization} confirm this trend). No
relevant code update was made during that period and logs indicated that the
brokers were able to perform faster. This is likely due to hardware upgrades
on the DTNs. The absence of continuous monitoring of those nodes does not
allow to quantify bottlenecks but spot measurements of their load indicate
that a faster CPU and better networking were likely responsible for the
improved performance. Investigations showed an average CPU load of 3.6\% on
the upgraded DTNs, as opposed to the ``high'' utilization reported by OLCF
for the previous DTNs. As such, further hardware upgrades seem unlikely to
improve significantly the performance of PanDA Brokers.\mtnote{Asked Segey
and Danila for values previous HW upgrade}
